
{\textbf{Product Catalogue Discovery Assistant (2 months) $\|$ US Fortune 500 Financial Services Client $\|$ Lead Data Scientist}
\begin{zitemize}
\item Designed and developed a RAG system on Databricks integrating Llama with LangChain to enable internal advisors to search and retrieve product information from internal catalogues.

\item Configured MLflow for experiment tracking and model versioning, with Unity Catalog managing the vector database for product embeddings and serving as the ML model registry.

\item Coordinated with compliance teams to establish data governance controls and regulatory guardrails, demonstrating improved information retrieval over traditional keyword search.

    
\end{zitemize}


{\textbf{Enterprise Q\&A Assistant (6 weeks) $\|$ US Fortune 500 Equipment Rental Firm $\|$ Lead Data Scientist}

\begin{zitemize}
\item Built a RAG chatbot using OpenAI GPT and LangChain to streamline sales team access to equipment manuals, pricing guides, and internal policies.

\item Collaborated with business stakeholders to align solution with operational requirements and validate response accuracy through iterative testing.

\item Delivered proof of concept demonstrating efficient handling of customer inquiries and reduced manual effort for complex queries.

\end{zitemize}

{\textbf{Clinical Data Support Q\&A Chatbot (6 weeks) $\|$ Healthcare Technology Startup $\|$ Data Scientist}}
\begin{zitemize}
\item Developed a Q\&A assistant using Anthropic Claude on AWS Bedrock to translate clustering algorithm outputs into natural language summaries for healthcare providers and researchers.

\item Applied prompt engineering to combine clustering results with structured patient data including symptoms, health conditions, and drug classifications from JSON files.

\item Partnered with design teams to enhance interface accessibility, delivering a proof of concept for extracting insights from complex bio-pharmaceutical datasets.
\end{zitemize}