

{\textbf{NLP for Safety Analytics (5 months) $\|$ US Fortune 500 Energy & Utility Client $\|$ Lead Data Scientist}}
\begin{zitemize}
\item Developed and deployed end-to-end NLP pipeline on Azure Databricks to process five years of safety incident reports from multiple sources in a unified data lake.

\item Implemented topic modelling and sentiment analysis to extract safety themes and trends from unstructured incident narratives across electricity and gas operations.

\item Deployed production solution with automated weekly reports and interactive dashboards enabling executives to filter insights by business unit and monitor emerging themes.

\item Solution received executive recognition and wide organisational adoption for providing actionable intelligence on safety policy and resource allocation.
\end{zitemize}


{\textbf{NLP for e-Discovery Document Classification (6 weeks) $\|$ Legal Services Client $\|$ Lead data Scientist}}
\begin{zitemize}
\item Developed proof of concept document classification system using Word2Vec embeddings and SVM classifiers on AWS SageMaker to automate legal document review processes.

\item Designed retraining pipeline framework to enable incremental model updates from newly labelled documents.

\item Demonstrated potential to reduce manual review hours and costs compared to traditional document review workflows.
\end{zitemize}

{\textbf{NLP for Global Procurement Standardisation (8 months) $\|$ US Fortune 500 Consumer Packaged Goods Company}}
\begin{zitemize}
\item Built text classification pipeline using Random Forest on Azure Machine Learning to automatically classify products into standardised global category templates across LATAM and North American procurement catalogues.

\item Collaborated with engineering teams to incorporate MLOps best practices including automated pipeline updates and model retraining workflows for production deployment.

\item Accelerated client's digital transformation roadmap by approximately one year by removing critical data standardisation bottleneck and improving data consistency across global operations.
\end{zitemize}
