\begin{enumerate}
% \item
% Eubank, S., {\textbf{Nath, M.}}, Mishra, R., and Adiga, A. (2023). Communities in directed weighted food networks using Moore-Shannon network reliability.
% (submitted Applied Network Science).

\item
Mishra, R., Eubank, S., {\textbf{Nath, M.}}, Amundsen, M., and Adiga, A. (2022, November).
{\href{https://link.springer.com/chapter/10.1007/978-3-031-21131-7_21}{\textcolor{blue}{
Community Detection Using Moore-Shannon Network Reliability: Application to Food Networks}}}, In International Conference on Complex Networks and Their Applications (pp. 271-282). Cham: Springer International Publishing. {\label{com-det}}

\item
Eubank, S., {\textbf{Nath, M.}}, Ren, Y., and Adiga, A. (2022).
{\href{https://arxiv.org/abs/2206.03550}{\textcolor{blue}{Perturbative methods for mostly monotonic probabilistic satisfiability problems}}}. arXiv preprint arXiv:2206.03550.
{\label{arxiv-paper}}

\item
{\textbf{Nath, M.,}} et. al. (2019).
{\href{https://link.springer.com/chapter/10.1007/978-3-030-05411-3_43}{\textcolor{blue}{
Using network reliability to understand international food trade dynamics}}}. In Complex Networks and Their Applications VII: Volume 1 Proceedings The 7th International Conference on Complex Networks and Their Applications COMPLEX NETWORKS 2018 7 (pp. 524-535). Springer International Publishing. {\label{trade}}

\item
{\textbf{Nath, M.}}, Ren Y., and Eubank, S. (2019). 
{\href{https://link.springer.com/chapter/10.1007/978-3-030-05411-3_44}{\textcolor{blue}{
An approach to structural analysis using Moore-Shannon network reliability}}}. In
Complex Networks and Their Applications VII: Volume 1 Proceedings The 7th International Conference on Complex Networks and Their Applications COMPLEX NETWORKS 2018 7 (pp. 537-549). Springer International Publishing. {\label{comp-theory}}

\item 
{\textbf{Nath, M.}}, Ren, Y., Khorramzadeh, Y., and Eubank, S. (2018).
{\href{https://www.sciencedirect.com/science/article/pii/S002251931730560X}{\textcolor{blue}{
Determining whether a class of random graphs is consistent with an observed contact network}}}. Journal of theoretical biology. 440, 121-132. {\label{epi-paper}}
 
\item
{\textbf{Nath, M.,}} and Eubank, S. (2018).
{\href{https://arxiv.org/abs/1807.06661}{\textcolor{blue}{
Model selection for sequential designs in discrete finite systems using Bernstein kernels}}}. arXiv preprint arXiv:1807.06661. {\label{old-arxiv}}

\item
Ren, Y., Eubank, S., and {\textbf{Nath, M.}}. (2016).
{\href{https://journals.aps.org/pre/abstract/10.1103/PhysRevE.94.042125}{\textcolor{blue}{
From network reliability to the Ising model: A parallel scheme for estimating the joint density of states}}}. Physical Review E, 94(4), 042125. {\label{ising}}

\item
{\textbf{M. Nath}}, et. al. (2015). 
{\href{https://link.springer.com/chapter/10.1007/978-3-319-16112-9_14}{\textcolor{blue}{
A two-parameter method to characterise the network reliability for diffusive processes}}}. In Complex Networks VI: Proceedings of the 6th Workshop on Complex Networks CompleNet 2015 (pp. 139-148). Springer International Publishing.

\item
Agarwala, A., {\textbf{Nath, M.}}, Lugani, J., Thyagarajan, K., and Ghosh, G. (2012).
{\href{https://journals.aps.org/pra/abstract/10.1103/PhysRevA.85.063606}{\textcolor{blue}{
Fock-space exploration by angle resolved transmission through a quantum diffraction grating of cold atoms in an optical lattice}}}. Physical Review A, 85(6), 063606.
% ({\textit{equal contribution as first author}}).
{\label{msc}}
\end{enumerate}