\begin{zitemize}
\item
Network reliability: a generic tool to explore diffusive processes on interacting systems, NASA Prebiotic Chemistry and Early Earth Environments (PCE3) Virtual Workshop 2022 Nano- to Cosmic- Studies of Complex Systems, University of Wisconsin Madison, Madison, WI, USA, 20 Oct, 2022.

\item
Perturbative methods for estimating relative contributions to network reliability, SIAM (Society for Industrial and Applied Mathematics) Workshop on Network Science, Virtual Workshop, 13-15 Sep, 2022.

\item
Statistical mechanical applications of graph dynamical systems, Condensed Matter Seminar, Department of Physics, Virginia Tech, Blacksburg, VA, USA, 30 Oct, 2017.

\item
Determining whether a particular contact network is consistent with a network model, 1st North American Social Networks Conference of the International Network for Social Network Analysis, Washington DC, USA, 26-30 Jul, 2017.

\item
Network reliability: A novel measure to study the effects of network topology on the diffusive dynamics, Symposium for the Society of Young Network Scientists, NetSci 2017, Indianapolis, IN, USA, 19-23 Jun, 2017.

\item
Network reliability: A measure to study diffusive dynamics on networks, Center for Soft Matter and Biological Physics Symposium 2017, Virginia Tech, Blacksburg, VA, USA, 17-18 May 2017.

\item
Effects of network structure on propagation of infectious diseases, 33rd Annual Graduate Student Assembly Symposium and Exposition, Virginia Tech, Blacksburg, VA, USA, 29 Mar 2017.

\item
Renormalisation group approaches for dynamics on irregular networks, American Physical Society (APS) March Meeting 2017, New Orleans, LA, USA, 13-17 Mar, 2017.

\item
Diffusive dynamics on a network, Southeastern Section of the American Physical Society (SESAPS) Conference 2016, Charlottesville, VA, USA, 9-12 Nov, 2016.

\item 
Effects of network structure on epidemic modeling, Biocomplexity Institute Symposium 2016, Virginia Tech, Blacksburg, VA, USA, 1 Nov, 2016.

\item
A two-parameter method to characterise the network reliability for diffusive processes, CompleNet 2015, New York City, NY, USA, 25-27 Mar, 2015.

\item
Four-parameter characterisation of network reliability and analysis of critical point phenomenology, APS (American Physical Society) March Meeting 2015, San Antonio, TX, USA, 2-6 Mar, 2015.

\end{zitemize}