

{\textbf{Data Modernisation to Databricks (3 months) $\|$ AI Engineer $\|$ Healthcare Client}}
\begin{zitemize}
\item Used Claude Code (Anthropic's AI coding assistant) to re-engineer legacy data pipelines and workflows into Databricks medallion architecture (a layered Bronze/Silver/Gold data model) on GCP, across patient journey and healthcare supply chain workstreams.

\item Migrated data from Salesforce, SAP, and cloud data warehouses into a unified Databricks platform with Unity Catalog (Databricks data governance layer), replacing manual metadata management with automated data quality checks and scalable orchestration.

\item Reduced data pipeline processing from 8–10 hours to near real-time and projected 25–35\% reduction in total cost of ownership by consolidating multi-environment workflows onto a single lakehouse platform.
\end{zitemize}

{\textbf{Product Catalogue Discovery Assistant (2 months) $\|$ US Fortune 500 Financial Services Client $\|$ Lead Data Scientist}}
\begin{zitemize}
\item Designed and developed a RAG (retrieval-augmented generation) system on Databricks integrating Llama with LangChain, enabling advisors to surface top product matches directly and reducing query resolution time compared to manual keyword search.

\item Configured MLflow for experiment tracking and model versioning, with Unity Catalog managing the vector database for product embeddings and serving as the ML model registry.

\item Coordinated with compliance teams to establish data governance controls and regulatory guardrails.
\end{zitemize}

% {\textbf{Enterprise Q\&A Assistant (6 weeks) $\|$ US Fortune 500 Equipment Rental Firm $\|$ Lead Data Scientist}
% \begin{zitemize}
% \item Built a RAG chatbot using OpenAI GPT and LangChain to streamline sales team access to equipment manuals, pricing guides, and internal policies.
% \item Collaborated with business stakeholders to align solution with operational requirements and validate response accuracy through iterative testing.
% \item Delivered proof of concept demonstrating efficient handling of customer inquiries and reduced manual effort for complex queries.
% \end{zitemize}

{\textbf{Clinical Data Support Q\&A Chatbot (6 weeks) $\|$ Healthcare Technology Startup $\|$ Data Scientist}}
\begin{zitemize}
\item Developed a Q\&A assistant using Anthropic Claude on AWS Bedrock to translate clustering algorithm outputs into natural language summaries for healthcare providers and researchers.

\item Applied prompt engineering to combine clustering results with structured patient data including symptoms, health conditions, and drug classifications from JSON files.

\item Partnered with design teams to enhance interface accessibility, delivering a proof of concept for extracting insights from complex bio-pharmaceutical datasets; subsequently adopted by the client for production development.
\end{zitemize}