
{\textbf{Data Lake Implementation on Snowflake (12 months) $\|$ Data Engineer $\|$ Nonprofit Organisation}}

\begin{zitemize}
 \item Maintained and upgraded a Snowflake data lake ingesting 2M daily FHIR (Fast Healthcare Interoperability Resources) records from 6 regional health information exchange networks, supporting programme analytics covering $\sim$5 million residents.

\item Built Snowflake task orchestrations and parameterised stored procedures for batch ingestion and export on daily, weekly, and monthly schedules, with data quality checks and compliance controls for sensitive patient data.

\item Refactored legacy monolithic JavaScript into modular Python and SQL, improving maintainability and enabling the pipeline to extend across additional source networks.

\end{zitemize}

{\textbf{Network Predictive Maintenance Solution (4 weeks) $\|$ Analytics Engineer $\|$ Major US Telecom Client}}

\begin{zitemize}
\item Developed statistical analysis combining 6 radio frequency (RF) performance metrics with geographical clustering to proactively identify faulty network infrastructure from user device data.

\item Implemented automated stored procedures on Google BigQuery processing 90-day network performance data across New York metropolitan area, collaborating with network engineers to validate preventive maintenance insights.

\item Projected $\sim$US \$8M annual operational cost savings through reduction of $\sim$30K customer support calls and $\sim$6K service visits, with methodology validated for nationwide scaling.

\end{zitemize}


{\textbf{Data Migration to Salesforce (5 months) $\|$ Data Engineer $\|$ Nonprofit Organisation}}
\begin{zitemize}
\item Migrated 1TB of historical data to Salesforce through custom SQL stored procedures, maintaining foreign key relationships across interdependent datasets of up to billions of rows.

\item Configured parameterised Azure Data Factory pipelines supporting full historical loads and incremental updates with table partitioning for large-scale dataset performance.

\item Built validation framework including row count verification, source-to-destination data comparison, and duplicate detection to ensure data integrity across migrations.
\end{zitemize}
