
%====================
% EXPERIENCE A
%====================

\subsection{{Slalom, Inc., New York, New York, USA}}
{\textit{Senior Data Scientist}} \hfill Sep 2024 -- Present
\\
{\textit{Data Scientist}} \hfill Jul 2021 -- Aug 2024
\\
{\textit{Associate Data Scientist}} \hfill Jan 2020 -- Jun 2021

\vspace{-0.25cm}

\begin{zitemize}
\item {\textbf{\textit{GenAI Projects}}}
\vspace{0.05cm}

{\textbf{Product Catalogue Discovery Assistant (2 months) $\|$ US Fortune 500 Financial Services Client $\|$ Lead Data Scientist}}
\begin{zitemize}
\item Designed and developed a RAG system on Databricks integrating Llama with LangChain to enable internal advisors to search and retrieve product information from internal catalogues.
\item Configured MLflow for experiment tracking and model versioning, with Unity Catalog managing the vector database for product embeddings, coordinating with compliance teams to establish data governance controls.
\end{zitemize}

{\textbf{Clinical Data Support Q\&A Chatbot (6 weeks) $\|$ Healthcare Technology Startup $\|$ Data Scientist}}
\begin{zitemize}
\item Developed Q\&A assistant using Anthropic Claude on AWS Bedrock to translate clustering algorithm outputs into natural language summaries for healthcare providers and researchers.
\item Applied prompt engineering to combine clustering results with structured patient data including symptoms, health conditions, and drug classifications from JSON files.
\end{zitemize}

\vspace{-0.1cm}

\item {\textbf{\textit{Key Data Science \& Data Engineering Projects}}}
\vspace{0.05cm}

{\textbf{NLP for Safety Analytics (5 months) $\|$ US Fortune 500 Energy Utility Client $\|$ Lead Data Scientist}}
\begin{zitemize}
\item Developed and deployed end-to-end NLP pipeline on Azure Databricks to process five years of safety incident reports, implementing topic modeling and sentiment analysis to extract safety themes from unstructured incident narratives.
\item Deployed production solution with automated weekly reports and interactive dashboards, receiving executive recognition and wide organizational adoption for providing actionable intelligence on safety policy and resource allocation.
\end{zitemize}

{\textbf{Data Lake Implementation on Snowflake (12 months) $\|$ Nonprofit Healthcare Organization}}
\begin{zitemize}
\item Maintained and upgraded Snowflake data lake processing 2M daily JSON bundles of statewide patient health information, building task orchestrations and parameterized stored procedures ensuring compliance with data protection regulations.
\item Refactored legacy monolithic JavaScript into modular Python and SQL components, improving maintainability and code quality.
\end{zitemize}

\end{zitemize}
